%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Laxman K R} \\[7.5pt]
AI Engineer $|$ Full-Stack Developer \\[4pt]
\href{https://github.com/thaletto}{\raisebox{-0.05\height}\faGithub\ thaletto} \ $|$ \ 
\href{https://linkedin.com/in/laxmanramesh}{\raisebox{-0.05\height}\faLinkedin\ laxmanramesh} \ $|$ \ 
\href{https://thaletto.vercel.app}{\raisebox{-0.05\height}\faGlobe \ portfolio} \ $|$ \ 
\href{mailto:krlaxman03@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ krlaxman03@gmail.com} \ $|$ \ 
\href{tel:+917448657412}{\raisebox{-0.05\height}\faMobile \ +91 7448657412} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
AI Engineer and Full-Stack Developer with experience building scalable products and agentic AI systems. Strong in TypeScript-led architecture, modern UI engineering, and Python-based AI workflows across production platforms.

%Work Experience
\section{Work Experience}


\begin{joblong}{Tata Consultancy Services (AI Engineer)}{Nov 2024 - Present}
\item \textbf{Agentic AMS Framework}: Engineered a self-healing system integrating Grafana and ServiceNow; built AI agents to diagnose incidents and execute SOP-driven remediations, reducing MTTR.
\item \textbf{Microfrontend Migration}: Drove migration of the TCS CBG AI platform to microfrontends, enabling independent release cycles and removing deployment bottlenecks.
\item \textbf{Google Cloud AI Offerings}: Led the development of a unified catalog platform to showcase AI offerings built across TCS using the Google Cloud stack, standardizing discovery and adoption.
\item \textbf{Team Leadership}: Owned release management and production stability as Deployment Lead; coordinated platform and frontend teams for reliable, high-performance delivery.
\end{joblong}
  
%Projects
\section{Projects}

\begin{joblong}{Agentic AMS Framework}{\href{https://thaletto.vercel.app/projects/ams}{[Blog]}}
\item Engineered a self-healing incident management platform using multi-agent workflows for triage, root-cause analysis, and automated remediation.
\item Integrated Grafana and ServiceNow to streamline incident detection, context enrichment, and SOP-driven resolution workflows.
\item Tech: Microsoft AutoGen, LangChain, FastAPI, Qdrant, MongoDB, Redis, Next.js, Docker.
\end{joblong}

\begin{joblong}{Google Cloud AI Offerings}{}
\item Developed a centralized platform to catalog and present enterprise AI solutions built across teams.
\item Improved internal discoverability and adoption by standardizing solution metadata, workflows, and access patterns.
\item Tech: Next.js, TypeScript, Python, FastAPI, Google Cloud Platform, Google Cloud Storage, PostgreSQL.
\end{joblong}


\begin{joblong}{Ascendant}{\href{https://pypi.org/project/astro-ascendant/}{[PyPI]}}
\item Developed and published \texttt{astro-ascendant}, a Python package for astrological chart and planetary position calculations.
\item Implemented high-accuracy ephemeris computation workflows using Swiss Ephemeris data for transit and natal chart use cases.
\item Built maintainable packaging and release automation to streamline publishing and version updates.
\item Tech: Python, Swiss Ephemeris, PyPI packaging, GitHub Actions.
\end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}X r@{}}
\textbf{B.Tech Computer Science and Engineering} & \normalsize Sep 2020 -- May 2024 \\
Amrita Vishwa Vidyapeetham, Coimbatore & \normalsize CGPA: 7.02/10 \\
Research: \textit{Complex or Irregular Lung Nodule Detection from CT Scans} & \href{https://thaletto.vercel.app/lung-nodule-detection.pdf}{[Link]}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages &  \normalsize{Python, TypeScript, JavaScript, Effect TS, Java, Kotlin}\\
AI/LLM &  \normalsize{AI SDK, Google ADK, Microsoft AutoGen, LangChain, Azure OpenAI}\\
Frontend &  \normalsize{Next.js, React, Tailwind CSS, Material UI}\\
Backend &  \normalsize{Node.js, Bun, Express, FastAPI}\\
Databases &  \normalsize{PostgreSQL, MongoDB, Redis, Qdrant}\\
Cloud/DevOps &  \normalsize{Google Cloud, Docker, Jenkins, Grafana, ServiceNow}\\
\end{tabularx}

% \vfill
% \center{\footnotesize Last updated: \today}

\end{document}
